\vfill World of Warcraft's New Way to Get You Hooked

### 2013-04-04 paper.tex
11. Added explicit metrics and outlines for public good arguments.
12. More WOT/quote cleaning in Public Good

First will be a purely numerical, Utilitarian approach to public good, `` ``Public Good'' By The Numbers''. I find this argument to be a bit heartless and cold and so I will follow it with a section that shows that the public good is not only upheld, but improved, by World of Warcraft, `` ``Public Good'' Being Improved''.

@@

\subsubsection{``Public Good'' Being Improved}
World of Warcraft has over 10 million subscribers \cite{WoWPlayerCount} who average 22 hours of play time per week. \cite{PlayerMotivations} A study published in \emph{Cyberpsychology \& Behavior} \cite{ExcessiveUseForSocialAspects} states, ``[i]t is clear that MMORPG users have a tendency to spend many more hours devoted to their game and find the social aspects of the in-game world more pleasant and satisfying than what occurs in the real world. However, MMORPG users do not seek self-confidence in-game, would find fun elsewhere if MMORPGs did not exist, and would not feel irritated if they did not have the chance to play for 1 day. This would suggest that, as much as MMORPG users enjoy the time they spend in-game, even more so than real-life activities with friends, they are not addicted.'' World of Warcraft players are passionate about their experiences in the game, but they do not show signs of addiction.

>>>>

First will be a purely numerical, Utilitarian approach to public good, `` ``Public Good'' By The Numbers''. The metric used will be the percentage of the population addicted to World of Warcraft. I find this argument to be a bit heartless and cold and so I will follow it with a section that shows that the public good is not only upheld, but improved, by World of Warcraft, `` ``Public Good'' Being Improved''. These improvements come from World of Warcraft helping some users overcome deficiencies in themselves, offering players powerful emotion experiences, and providing new or improved life skills.

@@

\subsubsection{``Public Good'' Being Improved}
World of Warcraft has over 10 million subscribers \cite{WoWPlayerCount} who average 22 hours of play time per week. \cite{PlayerMotivations} A study published in \emph{Cyberpsychology \& Behavior} \cite{ExcessiveUseForSocialAspects} shows that although World of Warcraft players are passionate about their experiences in the game, they do not show signs of addiction.
